---
title: "Lecture 4"
output: html_document
---

```{r setup, include=FALSE}

library(tidyverse)



library(tidyverse)
library(pROC)
library(lubridate)
library(broom)

```


```
```{r}
read_and_clean <- function(f){
  df <- read_csv(f, skip = 1) # Skip the first row
  df <- df[,-1] # Remove the first column
  col_names <- read_csv(f, n_max=0) %>% names() # Retrieve the column names as a separate csv file
  names(df) <- col_names
  return(df)
}


retrieve_data <- function(data_loc){
  # Get a list of all the files in data_loc
  files <- list.files(data_loc, full.names = TRUE)
  
  # Iterate through all files, applying the read_and_clean function
  list_df <- map(files, read_and_clean) 
  
  # Bind together the data frames
  df <- bind_rows(list_df)
  
  return(df)
}
```

```
```{r}
# Show first few rows
head(df)

### Plotting

df_clean <- df %>%
  select(Occupancy, Humidity, CO2, Temperature) %>%
  mutate(Occupancy = as.factor(Occupancy))

df %>% 
  filter(month(as_date(date)) == 2) %>% 
  ggplot(aes(x = date, y = Occupancy, fill = Occupancy)) + 
  geom_line(size = 1, color = 'darkgreen') + 
  theme_bw()


```

## Including Plots
```{r}

set.seed(456)

train_idx <- sample(1:nrow(df_clean), 0.8*nrow(df_clean))
train <- df_clean[train_idx,]
test <- df_clean[-train_idx,]


train %>%
  pivot_longer(Humidity:Temperature,
               names_to = 'variable') %>% 
  ggplot(aes(x = Occupancy, y = value)) + 
  geom_boxplot() + 
  facet_wrap(~variable, scales = 'free_y')


```



```
```{r}
log_reg <- glm(Occupancy ~ ., data = train, family = 'binomial')


test_pred <- test %>% 
  mutate(pred = predict(log_reg, newdata = test, type = 'response'),
         pred_class = as.integer(pred > 0.5),
         correct = pred_class == Occupancy) 
         
         
         
```

```
```{r}

classification_rate <- mean(test_pred$correct)
print(classification_rate)


```


