---
title: "Lecture 6"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

The data show metered electricity usage (kW) for 370 customers.

This data can be accessed at https://archive.ics.uci.edu/ml/datasets/ElectricityLoadDiagrams20112014

### Imports

```{r}
library(tidyverse)
library(lubridate)
library(broom)
```

### Set theme for plots 

```{r}
theme_set(theme_light())
```

### Read data

The data uses a slightly unusual format where:  

1. columns are separated by semi-colons
2. decimal points are given by commas

This format can be read with `read_csv2()`. 

```{r}
f <- 'data/LD2011_2014.txt'

df <- read_csv2(f) # data is separated by semi-colons, comma for decimals
names(df)[1] <- 'timestamp'
```


```{r}
# Clean data and reduce to Q3 and Q4
df_short <- df %>% 
  mutate(timestamp = ymd_hms(timestamp),
         hour = hour(timestamp),
         wday = wday(timestamp)) %>% # note that 1 --> Sunday, 2 --> Monday etc.
  filter(quarter(timestamp) %in% c(3,4)) %>%
  mutate_if(is.character, as.numeric)
```


### Confirm no columns have 0 variance

```{r}
(map_dbl(df_short, ~sd(.)) == 0) %>% sum()
```

### Transform: row for each customer, column for each wday/hour

```{r}
df_transform <- df_short %>% 
  pivot_longer(-c(timestamp, hour, wday),
               names_to = 'customer',
               values_to = 'kW') %>% 
  group_by(customer, wday, hour) %>%
  summarise(mean_kW = mean(kW)) %>%
  pivot_wider(names_from = c(wday, hour), 
              values_from = mean_kW) %>%
  ungroup()
```

### Normalise rows

```{r}
for (i in 1:nrow(df_transform)){
  max_value <- max(df_transform[i,-1])
  min_value <- min(df_transform[i,-1])
  df_transform[i,-1] <- (df_transform[i,-1] - min(df_transform[i,-1])) / (max_value - min_value)
}

df_transform
```


### Calculate the principal components 

```{r}
pcs <- df_transform %>% 
  select(-customer) %>% # remove non-numeric columns
  scale() %>% # standardise the data
  prcomp()

# Tidy! 
tidy_pcs <- tidy(pcs)
```


### Scree plot

```{r}
plot(pcs)
```


### Plot first 2 principal components

```{r}
pcs_2 <- tidy_pcs %>%
  filter(PC <= 2) %>% 
  pivot_wider(id_cols = row, 
              names_from = PC)

pcs_2 %>%
  ggplot(aes(x = `1`, y = `2`)) +
  geom_point() 
```

```{r}
set.seed(123)

k <- 3

clusters <- tidy_pcs %>%
  filter(PC <= 2)%>%
    pivot_wider(id_cols = row, 
              names_from = PC)%>%
  select(-row)%>%
  kmeans(k)

pcs_2_clusters <- pcs_2 %>%
  mutate(cluster = as.factor(clusters$cluster))
`
```



### Elbow plot

```{r}
set.seed(123)

ks <- 2:20
vs <- numeric()
for (k in ks){
  cls <- tidy_pcs %>%
  filter(PC <= 2) %>% 
    pivot_wider(id_cols = row, 
                names_from = PC) %>%
    select(-row) %>% 
    kmeans(k)
  vs <- c(vs, cls$tot.withinss)
}

plot(ks, vs, type = 'b', xlab = 'k', ylab = 'Total within-cluster sum of squares')

```


```{r}
# Add clusters to original time series
df_clusters <- df_transform %>% 
  mutate(cluster = as.factor(clusters$cluster))

# Pivot the data
df_clusters_pivot <- df_clusters %>%
  pivot_longer(contains('_')) %>% 
  group_by(customer) %>%
  mutate(index = row_number())

# Adding weekday and hour columns in order to facet_wrap on weekday
wday_hour <- str_split(df_clusters_pivot$name, '_', simplify=TRUE)
df_clusters_pivot$wday <- as.factor(wday_hour[,1])
df_clusters_pivot$hour <- as.integer(wday_hour[,2])
``` 



### Plot the mean consumption profiles for each cluster

```{r}
mean_power <- df_clusters_pivot %>% 
  group_by(cluster, wday, hour) %>% 
  summarise(mean_power = mean(value),
            upper = quantile(value, 0.75),
            lower = quantile(value, 0.25))

mean_power %>% 
  ggplot(aes(x = hour, 
             y = mean_power, 
             ymin = lower,
             ymax = upper,
             fill = cluster,
             colour = cluster)) + 
  geom_line() + 
  geom_ribbon(alpha = 0.2, color = NA) + 
  facet_wrap(~wday) +
  labs(subtitle = 'Line shows mean power (kW)\nRibbon shows inter-quartile range')
  
```





---
title: "Model Selection"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

### Imports

```{r}
library(tidyverse)
library(boot)
```

### Pre-process data

```{r}
f <- 'data/vw_train.csv'
train <- read_csv(f) %>% 
  drop_na() %>%
  mutate(washer_dryer = as.factor(
    if_else(str_detect(appliances, 'washer_dryer'), 1, 0)
    ))

colnames(train)

# Defining formulae to try
formulae <- c('washer_dryer ~ activePower + transient1',
              'washer_dryer ~ activePower + transient1 + transient2',
              'washer_dryer ~ current * voltage + transient1',
              'washer_dryer ~ activePower + current + voltage')

# K-fold CV 
errors <- numeric()
for (f in formulae){
  fit <- glm(as.formula(f), family = 'binomial', data = train)
  cv_fit <- cv.glm(train, fit, K = 10)
  errors <- c(errors, cv_fit$delta[1])
}

# Print the best formula
best_f <- formulae[which.min(errors)]
print(best_f)

```
