---
title: "Renewables Ninja"
output:
  html_document:
    df_print: paged
editor_options:
  chunk_output_type: console
---

### Imports

```{r}
library(tidyverse)
library(rpart)
library(randomForest)
```

### Reading the data

```{r}
ninja <- read_csv('data/ninja_IOE_solar_pv.csv', skip = 3)
```

### Date time conversions

```{r}
ninja <- ninja %>%
  mutate(date = lubridate::date(time),
         week = lubridate::week(time),
         hour = lubridate::hour(time)) 
```

### Plot mean electricity production by hour

```{r}
ninja %>% 
  ggplot(aes(x = hour, y = electricity)) + 
  stat_summary(geom = 'bar',
               fun = mean,
               fill = '#E69F00') + 
  stat_summary(geom = 'errorbar',
               fun.min = min,
               fun.max = max, 
               alpha = 0.5) + 
  theme_minimal()
```

### Autocorrelation plot 

```{r}
acf(ninja$electricity, lag.max = 96)
```


### Splitting test/train

```{r}
train <- ninja %>% filter(lubridate::month(time) < 10)
test <- ninja %>% filter(lubridate::month(time) >= 10)
```


### Sin and Cos Transforms of Week and Hour

```{r}
train %>% 
  mutate(sinweek = sin(2 * pi * week / 52),
         cosweek = cos(2 * pi * week / 52)) %>% 
  ggplot(aes(x  = sinweek, y = cosweek)) + 
  geom_point()
```

```{r}
train %>% 
  mutate(sinhour = sin(2 * pi * hour / 24),
         coshour = cos(2 * pi * hour / 24)) %>% 
  ggplot(aes(x  = sinhour, y = coshour)) + 
  geom_point() + 
  theme_light()
```

### Pre-Process Data

```{r}
prep_df <- function(df){
  df %>% 
    transmute(time, 
              electricity = electricity,
              electricity_24 = lag(electricity, 24),
              sinhour = sin(2 * pi * hour / 24),
              coshour = cos(2 * pi * hour / 24),
              sinweek = sin(2 * pi * week / 52),
              cosweek = cos(2 * pi * week / 52),
              temperature_24 = lag(temperature, 24),
              irradiance_direct_24 = lag(irradiance_direct, 24),
              irradiance_diffuse_24 = lag(irradiance_diffuse, 24)) 
}

train_prep <- prep_df(train) %>% drop_na()
test_prep <- prep_df(test)
```

### Fit models

```{r}
linear_model <- lm(electricity ~ . - time, train_prep)
decision_tree <- rpart(electricity ~ . - time, train_prep,
                       minsplit = 10)
random_forest <- randomForest(electricity ~ . - time, 
                              data = train_prep,
                              ntree = 200)
```

### Calculate RMSE (training data)

```{r}
rmse <- function(actual, predicted){
  mse <- mean((actual - predicted) ** 2)
  return(sqrt(mse))
}

train_preds <- train_prep %>% 
  transmute(
        time,
        actual = electricity,
        persistence = electricity_24,
        linear_model = predict(linear_model, .),
        decision_tree = predict(decision_tree, .),
        random_forest = predict(random_forest, .))

train_preds %>% 
  pivot_longer(persistence:random_forest) %>% 
  group_by(name) %>% 
  summarise(rmse = rmse(actual, value))
```


### Plot predicted vs. actual

```{r}
train_preds %>% 
  right_join(train, by = 'time') %>% 
  pivot_longer(persistence:random_forest,
               names_to = 'model') %>% 
  ggplot(aes(x = electricity, 
             y = value, 
             color = as.factor(lubridate::quarter(time)))) + 
  geom_point(size = 0.4, alpha = 0.7) + 
  geom_abline(intercept = 0, slope = 1, color = 'blue') +
  facet_wrap(~model) + 
  theme_light() + 
  labs(x = 'Actual',
       y = 'Predicted', 
       color = 'Quarter')

```

### Plot residuals for random forest

```{r}
random_forest_df <- train_prep %>% 
  drop_na() %>% 
  mutate(random_forest = predict(random_forest, .),
         residual = random_forest - electricity) 

random_forest_df %>%
  ggplot(aes(x = time, y = residual)) + 
  geom_point(size = 0.7, alpha = 0.5) + 
  geom_smooth(method = 'loess') + 
  theme_light() + 
  labs(title = 'Residuals of Random Forest model')
```

### Autocorrelation of residuals

```{r}
acf(random_forest_df$residual, lag.max = 24)
```


### Test predictions 

```{r}
preds_df <- test_prep %>% 
  mutate(linear_model = predict(linear_model, test_prep),
            decision_tree = predict(decision_tree, test_prep),
            random_forest = predict(random_forest, test_prep),
            persistence = electricity_24)
```

### Function for plotting random day

```{r}

plot_random_day <- function(model_name){
  # Sample a random date
  random_date <- sample(unique(date(preds_df$time)), 1)

  preds_df %>% 
    filter(date(time) == random_date) %>% # filter to the date
    select(time, electricity, model_name) %>% # select specified model and the actual values
    pivot_longer(electricity:model_name) %>% # pivot  
    ggplot(aes(x = time, y = value, color = name)) + 
    geom_line() + 
    theme_light()
}

plot_random_day('linear_model')


```


### Calculate RMSE (test)

```{r}
preds_df %>% 
  drop_na() %>%
  pivot_longer(linear_model:persistence,
               names_to = 'model') %>% 
  group_by(model) %>% 
  summarise(rmse = rmse(electricity, value))
```



